\bf Tuning parameter selection for a penalized estimator of species richness

### 2019-08-08 rre_manuscript/paper.tex
mike's inline suggestions

We also applied our method to estimate the species-level diversity of human host associated microbes.
\cite{pasolli2019extensive} assembled 4,930 species-level genome bins (SGBs) using publicly available shotgun metagenomic data, but we expect that many SGBs were not observed due to undersampling and challenges in genome assembly. The frequency counts of each SGB are available at \cite[Table S4]{pasolli2019extensive}.

@@

>>>>

We also applied our method to estimate the species-level diversity of human host associated microbes.
\cite{pasolli2019extensive} assembled $c=4,930$ species-level genome bins (SGBs) using publicly available shotgun metagenomic data, but we expect that many SGBs were not observed due to undersampling and challenges in genome assembly. The frequency counts of each SGB are available at \cite[Table S4]{pasolli2019extensive}.

@@

We found that $\widehat{C}_{[0]} = 420056$ with $(\hat{\alpha}, \hat{\delta}) = (0.00234, 0.00641).$
